---
title: "databits-survey-2019-results"
date: '`r format(Sys.Date(), "%Y-%m-%d")`'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries, include=FALSE}
library(tidyverse)
library(googlesheets)
library(kableExtra)
```

```{r, include=FALSE}
# surveyResultsToken <- gs_url('https://docs.google.com/spreadsheets/d/1UU0FtgoN1tSjY1qaXcWSEdcsVRRCCFNZ5huDSTLuKag/edit?usp=sharing')
# surveyResults <- gs_read(surveyResultsToken, ws = 1)
# write_csv(surveyResults, "surveyResults.csv")
surveyResults <- read_csv('surveyResults.csv')
colnames(surveyResults)[2] <- "recentlyRead"
colnames(surveyResults)[3] <- "increaseInterest"
colnames(surveyResults)[4] <- "topicsOfInterest"
colnames(surveyResults)[5] <- "interestToWrite"
colnames(surveyResults)[6] <- "increaseContribution"
colnames(surveyResults)[7] <- "optimalLength"
colnames(surveyResults)[8] <- "format"
colnames(surveyResults)[9] <- "notification"
colnames(surveyResults)[10] <- "shareOutside"
colnames(surveyResults)[11] <- "communityValue"
colnames(surveyResults)[12] <- "addtionalThoughts"
```

<br>
<hr>
#### Have you read the two most recent Databits issues (spring 2018 and summer 2019)?

```{r recentlyRead, echo=FALSE}

surveyResults %>% 
  count(recentlyRead) %>%
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### If reading Databits has not interested you, what might increase your interest?

```{r increaseInterest, echo=FALSE}

surveyResults %>% 
  select(increaseInterest) %>% 
  filter(!is.na(increaseInterest)) %>% 
  mutate(response = "-") %>%
  select(response, increaseInterest) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### What topics do you like to read about in Databits, select all that are appropriate?

```{r topicsOfInterest, echo=FALSE}

surveyResults %>% 
  select(topicsOfInterest) %>% 
  mutate(topicsOfInterest = strsplit(topicsOfInterest, ",")) %>% 
  unnest(topicsOfInterest) %>% 
  filter(
    grepl("SiteBytes|Personnel|International|Recaps|Recommendations|op-eds|analyses|history", topicsOfInterest, ignore.case = T)
  ) %>% 
  mutate(
    topicsOfInterest = str_trim(topicsOfInterest, side = c("both")),
    topicsOfInterest = case_when(
      grepl("recaps from meet", topicsOfInterest, ignore.case = T) ~ "Recaps from meetings, working groups, and Slack conversations",
      grepl("op-eds", topicsOfInterest, ignore.case = T) ~ "Op-eds, reflections, and commentaries",
      grepl("cool graphs", topicsOfInterest, ignore.case = T) ~ "Analyses of interest",
      grepl("Reading recommendations", topicsOfInterest, ignore.case = T) ~ "Reading recommendations",
      TRUE ~ topicsOfInterest
    )
  ) %>% 
  count(topicsOfInterest) %>% 
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### What topics might you be interested to write about in Databits, either for an IM or broader audience?

```{r interestToWrite, echo=FALSE}

surveyResults %>% 
  select(interestToWrite) %>% 
  mutate(interestToWrite = strsplit(interestToWrite, ",")) %>% 
  unnest(interestToWrite) %>% 
  filter(
    grepl("SiteBytes|Personnel|International|Recaps|Recommendations|op-eds|analyses|history", interestToWrite, ignore.case = T)
  ) %>% 
  mutate(
    interestToWrite = str_trim(interestToWrite, side = c("both")),
    interestToWrite = case_when(
      grepl("recaps from meet", interestToWrite, ignore.case = T) ~ "Recaps from meetings, working groups, and Slack conversations",
      grepl("op-eds", interestToWrite, ignore.case = T) ~ "Op-eds, reflections, and commentaries",
      grepl("cool graphs", interestToWrite, ignore.case = T) ~ "Analyses of interest",
      grepl("Reading recommendations", interestToWrite, ignore.case = T) ~ "Reading recommendations",
      TRUE ~ interestToWrite
    )
  ) %>% 
  count(interestToWrite) %>% 
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### If you are not interested to contribute a story, can you envision any changes that would make you more likely to contribute?

```{r increaseContribution, echo=FALSE}

surveyResults %>% 
  select(increaseContribution) %>% 
  filter(!is.na(increaseContribution)) %>% 
  mutate(response = "-") %>%
  select(response, increaseContribution) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```


<hr>
#### What is an optimal length for Databits stories, both in terms of the length of story you would like to read and to write?

```{r optimalLength, echo=FALSE}

surveyResults %>% 
  select(optimalLength) %>% 
  filter(!is.na(optimalLength)) %>% 
  mutate(optimalLength = strsplit(optimalLength, ",")) %>% 
  unnest(optimalLength) %>% 
  mutate(optimalLength = str_trim(optimalLength, side = c("both"))) %>% 
  count(optimalLength) %>%
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### There has been lively discussion about the format of Databits (i.e., PDF or a blog model). For the editors, it comes down to continuous versus discrete publishing models. Would you be more likely to read Databits articles if they are distributed first:

```{r format, echo=FALSE}

surveyResults %>% 
  select(format) %>% 
  filter(!is.na(format)) %>% 
  count(format) %>%
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### How would you like to hear about new Databits content if it were published continuously (as in a blog)?

```{r notification, echo=FALSE}

surveyResults %>% 
  select(notification) %>% 
  mutate(notification = strsplit(notification , ",")) %>% 
  unnest(notification) %>% 
  mutate(notification = str_trim(notification , side = c("both"))) %>% 
  count(notification) %>% 
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
##### Do you share Databits content outside of the IM community?

```{r shareOutside, echo=FALSE}

surveyResults %>% 
  select(shareOutside) %>% 
  filter(!is.na(shareOutside)) %>% 
  count(shareOutside) %>%
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### What do you think is Databits’ value to the IM community?

```{r communityValue, echo=FALSE}

surveyResults %>% 
  select(communityValue) %>% 
  filter(!is.na(communityValue)) %>% 
  mutate(communityValue = strsplit(communityValue, ",")) %>% 
  unnest(communityValue) %>% 
  filter(
    grepl("overview|ideas|shared|sandbox|platform|sharable", communityValue, ignore.case = T)
  ) %>% 
  mutate(
    communityValue = str_trim(communityValue, side = c("both")),
    communityValue = case_when(
      grepl("sharable", communityValue, ignore.case = T) ~ "provides sharable, citable record of IM work for disseminating to wider community",
      grepl("sandbox", communityValue, ignore.case = T) ~ "provides a sandbox for new projects, possibly for subsequent publications",
      TRUE ~ communityValue
    )
  ) %>% 
  count(communityValue) %>% 
  arrange(desc(n)) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```

<hr>
#### Please provide any additional thoughts that you would like to share, and note that we are receptive to strong, even inflammatory, opinions so please feel free to comment openly.

```{r addtionalThoughts, echo=FALSE}

surveyResults %>% 
  select(addtionalThoughts) %>% 
  filter(!is.na(addtionalThoughts)) %>% 
  mutate(response = "-") %>%
  select(response, addtionalThoughts) %>% 
  kableExtra::kable() %>% 
  kable_styling(bootstrap_options = c("striped", "condensed"), full_width = F, position = "left")
```